%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Neural Net Committee Lead} % Job title
    {Sustainable Recycling Project - Samsung Solve for Tomorrow} % Organization
    {Durham, NC} % Location
    {Jan. 2020 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Won National Finalist Prize of \$150,000 in technology and supplies for NC School of Science and Math.}
        \item {Created an app using Flutter that uses image processing and machine learning algorithms to help people separate recyclables and non-recyclables.}
        \item {Trained models using Yolov3 and tflite for TensorFlow which allowed for real-time, multiple object detection using a top down approach (looks at a whole photo instead of pixel by pixel).}
        \item {Part of the three person national pitch presentation team, delivered layman explanation and overview of testing and evaluation methods.}
        \item {Led development of frontend React scanning software with custom Real-Time ML to capture a clean image automatically.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Personal Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

  %---------------------------------------------------------
    \cvhonor
      {Flower Identification Network} % Award
      {Another classification network that differentiated between 133 species of flowers with multiple objects detection in real-time.} % Event
      {} % Location
      {2019} % Date(s)
  
  %---------------------------------------------------------
    \cvhonor
      {SiRI/STRI/WebAssignHW} % Award
      {Collection of programs that keep track of upcoming assignments on various Learning Management Systems and add them to a task manager.} % Event
      {} % Location
      {2018-2020} % Date(s)
  
  %---------------------------------------------------------
    \cvhonor
      {Reverse Engineering iOS apps} % Award
      {Reverse engineered multiple iOS apps and injected custom dylibs to load on launch and modify various parameters of the application.} % Event
      {} % Location
      {2020} % Date(s)
  
  %---------------------------------------------------------
    \cvhonor
      {IoT Garage Door Opener} % Award
      {Constructed a HomeKit compatible garage door opener from a low-cost Wi-Fi SoC, relays, and magnetic sensors to detect state.} % Event
      {} % Location
      {2018} % Date(s)
  
  %---------------------------------------------------------
  \end{cvhonors}